Determining what makes some TADs unpredictable

### 2019-04-12 Scripts/investigating_misclassified_TADs.Rmd
editted script for investigating misclassified tads

@@

ggplot(predictiondata_gm12878_10kb, aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

>>>>

#Wilcoxon test on differences in distances between FN and TP
FNdata <- FNdata[,-1]
TPdata <- TPdata[,-1]
wilcoxon.results <- numeric(length(colnames(FNdata)))
for(i in 1:length(colnames(FNdata))){
 wilcoxon.results[i] <- wilcox.test(FNdata[,i],TPdata[,i])$p.value
}
wilcox.table <- cbind.data.frame(Annotation=gsub("_dist","",colnames(FNdata)), Wilcoxon.PValue=wilcoxon.results)
wilcox.table <- wilcox.table[order(wilcox.table$Wilcoxon.PValue, decreasing = FALSE),]
wilcox.table$Wilcoxon.PValue <- round(wilcox.table$Wilcoxon.PValue,7)

@@

#Ploting densities
ggplot(predictiondata_gm12878_10kb, aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
